---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HIDeM

<!-- badges: start -->
<!-- badges: end -->

The goal of HIDeM is to perform variable selection in an illness-death model with interval-censored time to illness. 

## Installation

You can install the development version of HIDeM from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arianebercu/HIDeM")
```

## Tutorials 

For the scenarios presented in the scientific paper, see the [tutorial vignette 1 ](https://github.com/arianebercu/HIDeM/doc/Reg-IDM-ICT-example.htlm)

```{r tutorial}
vignette("Reg-IDM-ICT-example", package = "HIDeM")
```
For an application on simulated data following Paquid cohort, see the [tutorial vignette 2](https://github.com/arianebercu/HIDeM/doc/Reg-IDM-ICT-example.htlm)

```{r tutorial2}
vignette("Reg-IDM-ICT-Paq1000", package = "HIDeM")
```

