---
title: "Example of regularized illness-death model on simulated data set"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reg-IDM-ICT-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Install the package

The HIDeM package is avaible on github, using the following commands : 
```{r setup,eval=F}
remotes::install_github("arianebercu/HIDeM", build_vignettes=T)
```

The HIDeM package depends on other R package, namely :

- lava (>= 1.4.1),
- mvtnorm (>= 1.0-3),
- marqLevAlg (> 2.0), 
- doParallel, 
- foreach, 
- parallel, 
- MASS,
- graphics, 
- grDevices, 
- stats, 
- ggplot2,
- pracma

We are using foreach, parallel and doParallel for parallelizing some time consuming functions, mvtnorm for generating random parameters in simulation, marqLevAlg (>2.0) for the numerical optimization. 

License: GPL (>= 2)
RoxygenNote: 7.3.2
Encoding: UTF-8

## Simulation interval censored data 

We have a sample of N=2000 individuals, followed during 18 years with visit scheduled every 2.5 years (+0.5 variability) and at each visit a probability of being lost to follow-up of 5\%. 

In IDM, we simulate transition intensities defined as, 
\begin{equation*} \label{eq:2}
\forall hl \in 01,02,12, \quad \quad \quad
\alpha_{hl}(t|\theta_{hl},\beta_{hl}, Z_{hl}) = \alpha_{0,hl}(t|\theta_{hl})e^{\beta_{hl}^\top Z_{hl}}
\end{equation*}

In this example, we choose to simulate 50 covariates having an independent Gaussian distribution (centered and reduced), $Z_{01}=Z_{02}=Z_{12}=Z$. Each covariate has a transition specific effect, on transition healthy $\rightarrow$ diseased $\beta_{01}$, healthy $\rightarrow$ deceased $\beta_{02}$ and diseased $\rightarrow$ deceased $\beta_{12}$. 

```{r echo=FALSE, results='asis'}
library(knitr)

# Define the table data as a matrix or data frame
tab <- data.frame(
  Transition = c(
    "$0 \\rightarrow 1$", "$0 \\rightarrow 2$", "$1 \\rightarrow 2$"
    ),
  
   `\\( \\beta_1 \\)` = c(0.8, 0, 0),
  `\\( \\beta_2 \\)` = c(0.8, 0.8, 0.8),
  `\\( \\beta_3 \\)` = c(0.8, 0.8, 0),
  `\\( \\beta_4 \\)` = c(0, 0, 0),
   `...` = rep("", 3),  
  `\\( \\beta_{10} \\)` = c(0, 0, 0),
  `\\( \\beta_{11} \\)` = c(-0.8, 0, 0),
  `\\( \\beta_{12} \\)` = c(-0.5, 0,-0.5),
  `\\( \\beta_{13} \\)` = c(-0.5, 0.5, 0),
  `\\( \\beta_{14} \\)` = c(0, 0, 0),
   `...` = rep("", 3),  
  `\\( \\beta_{20} \\)` = c(0, 0, 0),
  `\\( \\beta_{21} \\)` = c(0, -0.8, 0),
  `\\( \\beta_{22} \\)` = c(0, -0.5, -0.5),
  `\\( \\beta_{23} \\)` = c(0, 0, -0.8),
  `\\( \\beta_{24} \\)` = c(0, 0, 0),
   `...` = rep("", 3),  
  `\\( \\beta_{30} \\)` = c(0, 0, 0),
  check.names = FALSE
  
)
kable(tab, format = "html", escape = FALSE, caption = "")

tab <- data.frame(
  Transition = c(
    "$0 \\rightarrow 1$", "$0 \\rightarrow 2$", "$1 \\rightarrow 2$"
    ),
  
  `\\( \\beta_{31} \\)` = c(0, 0.8, 0),
  `\\( \\beta_{32} \\)` = c(0, 0.8, 0.8),
  `\\( \\beta_{33} \\)` = c(0, 0, 0.8),
  `\\( \\beta_{34} \\)` = c(0, 0, 0),
   `...` = rep("", 3),  
  `\\( \\beta_{40} \\)` = c(0, 0, 0),
  `\\( \\beta_{41} \\)` = c(0, 0, -0.5),
  `\\( \\beta_{42} \\)` = c(-0.5, 0.5, -0.5),
  `\\( \\beta_{43} \\)` = c(0, 0.5, 0),
  `\\( \\beta_{44} \\)` = c(0, 0, 0),
   `...` = rep("", 3),  
  `\\( \\beta_{50} \\)` = c(0, 0, 0),
  check.names = FALSE
  
)


# Print the table using kable for HTML output
kable(tab, format = "html", escape = FALSE, caption = "")

```

Following, the baseline transition intensity follows a Weibull distribution,
$$\displaystyle {\alpha_{0,hl}(t|\theta_{1,hl},\theta_{2,hl})=\theta_{1,hl}\theta_{2,hl}(\theta_{2,hl}t)^{\theta_{1,hl}-1}}$$

such that, $(\theta_{1,01},\theta_{2,01})=(3.4,0.075)$,$(\theta_{1,02},\theta_{2,02})=(3.4,0.085)$ and $(\theta_{1,12},\theta_{2,12})=(3.4,0.07)$. 
```{r }
library(HIDeM)
n_var<-50

BETA01<-rep(0,n_var)
BETA02<-rep(0,n_var)
BETA12<-rep(0,n_var)

BETA01[1:3]<-c(0.8,0.8,0.8)
BETA02[1:3]<-c(0,0.8,0.8)
BETA12[1:3]<-c(0,0.8,0)

BETA01[11:13]<-c(-0.8,-0.5,-0.5)
BETA02[11:13]<-c(0,0,0.5)
BETA12[11:13]<-c(0,-0.5,0)

BETA01[21:23]<-c(0,0,0)
BETA02[21:23]<-c(-0.8,-0.5,0)
BETA12[21:23]<-c(0,-0.5,-0.8)

BETA01[31:33]<-c(0,0,0)
BETA02[31:33]<-c(0.8,0.8,0)
BETA12[31:33]<-c(0,0.8,0.8)

BETA01[41:43]<-c(0,-0.5,0)
BETA02[41:43]<-c(0,0.5,0.5)
BETA12[41:43]<-c(-0.5,-0.5,0)

id02<-paste0("X",which(BETA02!=0))
id01<-paste0("X",which(BETA01!=0))
id12<-paste0("X",which(BETA12!=0))

cov<-matrix(0,ncol=n_var,nrow=n_var)
diag(cov)<-1

#scale.waittime=0.18,shape.waittime=1.8,
#scale.lifetime=0.15,shape.lifetime=2.3,
#scale.illtime=0.14,shape.illtime=2.2,
rep<-1
simu<-HIDeM::simulateIDM(n=2000,seed=rep,
                  scale.waittime=0.07,shape.waittime=3.4,
                  scale.lifetime=0.085,shape.lifetime=3.4,
                  scale.illtime=0.075,shape.illtime=3.4,
                  prob.censoring=0.05,
                  n.inspections=8,
                  administrative.censoring = 18,
                  schedule=2.5,punctuality=0.5,nvar=n_var,mean=rep(0,n_var),cov=cov,
                  x01=id01,x02=id02,x12=id12,
                  beta01=BETA01[BETA01!=0],beta02=BETA02[BETA02!=0],
                  beta12=BETA12[BETA12!=0])
```

In the output $simu$, you have two elements : the dataset \$data and explanatory plots \$plot. 
```{r}
head(simu$data)
library(gtsummary)
library(gt)
library(dplyr)
var<-paste0("X",c(1:n_var))
summaries<-simu$data[,!colnames(simu$data)%in%var]  %>%
  mutate(illstatus = ifelse(illstatus==1,"Ill","Healthy"),
          id.nodem.death=ifelse(id.nodem.death==1,"Yes","No"))%>%
   rename("L = time of last visit illness-free" = L)%>%
   rename("R = diagnosis visit time" = R)%>%
  rename("illstatus = true indicator of illness "=illstatus)%>%
   rename("observed.lifetime = time of death" = observed.lifetime)%>%
  rename("lifetime = time of death with IC on illness" = lifetime)%>%
  rename("T01 = simulated time on transition to illness"=T01)%>%
 rename("T02 = simulated time on transition to death illness-free"=T02)%>%
rename("T12 = simulated time on transition to death with illness"=T12)%>%
  rename("administrative.censoring = 18"=administrative.censoring)%>%
  rename("censtime = simulated last visit"=censtime)%>%
  rename("id.nodem.death = illness not observed due to death"=id.nodem.death)%>%
   mutate(seen.ill = ifelse(seen.ill==1,"Ill","Healthy"),
          seen.exit=ifelse(seen.exit==1,"Death","Alive"))%>%
   tbl_strata(
     strata = seen.ill,
     .tbl_fun =
       ~ .x %>%
       tbl_summary(by = seen.exit,
                   type = list(where(is.numeric) ~ "continuous2"),
                   statistic = list(
                     all_categorical() ~ "{n} ({p}%)"
                   ),
                   digits = all_continuous() ~ 2),
     .header = "**{strata}**, N = {n}"
   ) %>%
    modify_caption("Characteristics of individuals in simulated dataset")
summaries
```

In $data, we have a line per individual observation with : 

- seen.ill : observed illness (=1, ill)
- seen.exit : indicator of death (=1, dead)
- L : time of last visit illness-free (last visit for healthy individual)
- R : diagnosis visit time (r=l for healthy individual)
- observed.lifetime : time of death (18 for alive individual)
- illstatus : true indicator of illness (without interval censoring)
- lifetime : time of death knowing illstatus (without interval censoring)
- T01 : simulated time on transition $0 \rightarrow 1$
- T02 : simulated time on transition $0 \rightarrow 2$
- T12 : simulated time on transition $1 \rightarrow 2$
- id.nodem.death : illness not observed due to death (=1 if true)


In \$plot, we have 7 elements : 

- [[1]] : survival baseline intensity simulated on each transition 
- [[2]] : table of individual survival for transition $0 \rightarrow 1$ at given time points
- [[3]] : plot of 3 individual survival for transition $0 \rightarrow 1$ at given time points (id=1,2 and 3)
- [[4]] : table of individual survival for transition $0 \rightarrow 2$ at given time points
- [[5]] : plot of 3 individual survival for transition $0 \rightarrow 2$ at given time points (id=1,2 and 3)
- [[6]] : table of individual survival for transition $1 \rightarrow 2$ at given time points
- [[7]] : plot of 3 individual survival for transition $1 \rightarrow 2$ at given time points (id=1,2 and 3)

```{r,fig.width=6}
simu$plot[[1]]
head(simu$plot[[2]])
simu$plot[[3]]
head(simu$plot[[4]])
simu$plot[[5]]
head(simu$plot[[6]])
simu$plot[[7]]
```

## Run IDM-ICT 

In this section, we will explicit the profile likelihood, with:

- an outer loop on penalty parameters noted $(a,\lambda_{01},\lambda_{02},\lambda_{12})$, and 
- an inner loop on regression parameters $(\beta_{01},\beta_{02},\beta_{12})$ and baseline intensity parameters $(\theta_{01},\theta_{02},\theta_{12})$

Firstly, we need to perform a pre-selection of penalty parameters for each transition separately. For each transition, we first fit multi-state models including covariates only in the transition from state $h$ to $l$ ($hl \in \{01,02,12\}$), and considering a grid of $\lambda_{hl}$ with equidistant values from  0.0001 and 100 while keeping $a$ fixed at 1. It is recommended to try multiple values of $a$ in $]0,1]$, but for this example we will limit to lasso penalty (a=1). 

We choose to estimate the baseline intensity transition with M-spline basis with nodes at 0, 9 and 18 years of follow-up. To have relevant starting values for baseline intensities parameters of M-splines, we run a model without covariates. 

```{r,eval=F}

  
  mvoidexample <-HIDeM::  idm(formula02 = Hist(time = observed.lifetime, event = seen.exit) ~1,
                       formula01 = Hist(time = list(L,R), event = seen.ill) ~ 1,
                       formula12 = ~ 1,data=simu$data,eps=c(7,4,1), method="splines",maxiter=100)
  
  start<-c(mvoidexample$theta01,mvoidexample$theta02,mvoidexample$theta12,rep(0,50))
  
  nlambda<-20
  a <- 1
  lambdatest<-seq(0.01,100,length.out=nlambda)
  penalty<-ifelse(a==1,"lasso","elasticnet")

  alpha01<-list(rep(a,nlambda),1,1)
  alpha02<-list(1,rep(a,nlambda),1)
  alpha12<-list(1,1,rep(a,nlambda))
  alpha_all<-list(rep(a,3),rep(a,3),rep(a,3))
  
############################ 01 ################################################
    f02<-as.formula("Hist(time = observed.lifetime, event = seen.exit) ~1")
  f01<-as.formula(paste0("Hist(time = list(L,R), event = seen.ill) ~",paste0(paste0("X",seq(1:50)),collapse="+")))
  f12<-as.formula("~1")
  
  m01example <-HIDeM::  idm(formula02 = f02,
                                    formula01 = f01,
                                    formula12 = f12,data=simu$data,
                                    penalty=penalty,eps=c(7,4,1),
                                    lambda01 = lambdatest,
                                    lambda02=0.0001,
                                    lambda12=0.0001,B=start,
                                method="splines",nproc=2,clustertype = "PSOCK",
                                alpha=alpha01,maxiter=100,maxiter.pena = 2)
  

################################ 02 ############################################

  f02<-as.formula(paste0("Hist(time = observed.lifetime, event = seen.exit) ~",paste0(paste0("X",seq(1:50)),collapse="+")))
  f01<-as.formula("Hist(time = list(L,R), event = seen.ill) ~ 1")
  f12<-as.formula("~1")
#setwd("C:/Users/ab17/Desktop/CURTA/SMOOTH_HAZARD/OPTIM_B_DIFFLAMBDA_derivaana_all/Weibull_simu/Scenario1")

  m02example <-HIDeM::  idm(formula02 = f02,
                                    formula01 = f01,
                                    formula12 = f12,data=simu$data,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                    lambda02 = lambdatest,
                                    lambda01=0.0001,
                                    lambda12=0.0001,B=start,nproc=2,clustertype = "PSOCK",
                                alpha=alpha02,maxiter=100,maxiter.pena = 2)
  


######################################## 12 ###################################

  f02<-as.formula("Hist(time = observed.lifetime, event = seen.exit) ~1")
  f01<-as.formula("Hist(time = list(L,R), event = seen.ill) ~ 1")
  f12<-as.formula(paste0("~",paste0(paste0("X",seq(1:50)),collapse="+")))

  m12example <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=simu$data,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                lambda01 = 0.0001,
                                lambda12= lambdatest,
                                lambda02=0.0001,B=start,nproc=2,clustertype = "PSOCK",
                                alpha=alpha12,maxiter=100,maxiter.pena = 2)
  
  
```
The ouput of each models can be displayed using standard function such as print and summary : 
```{r}
m01example<-HIDeM::m01example
m02example<-HIDeM::m02example
m12example<-HIDeM::m12example
#print(m01example)
#summary(m01example)

#print(m02example)
#summary(m02example)

#print(m12example)
#summary(m12example)
```
The following step is to visualize the Bayesian Indicator Criteria (BIC) and determine the 3 values of $\lambda$ per transition minimizing it : 

```{r,fig.width=6}

plot(m01example$lambda[1,],m01example$BIC,xlab="Lambda values for 0 -> 1",ylab="BIC")
plot(m02example$lambda[2,],m02example$BIC,xlab="Lambda values for 0 -> 2",ylab="BIC")
plot(m12example$lambda[3,],m12example$BIC,xlab="Lambda values for 1 -> 2",ylab="BIC")

lambda01<-lambda02<-lambda12<-rep(NA,3)

############################## 01 ##############################################
BIC01<-sort(m01example$BIC[m01example$converged==1])[1:3]
BIC01<-na.omit(unique(BIC01))
  
  id<-which(m01example$BIC%in%BIC01)
  if(length(id)>3){
    lambda<-m01example$lambda[1,id]
    lambda01[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda01[1:3]<-m01example$lambda[1,id]
      lambda01<-na.omit(lambda01)
  }
  
############################## 02 ##############################################
BIC02<-sort(m02example$BIC[m02example$converged==1])[1:3]
BIC02<-na.omit(unique(BIC02))
  
  id<-which(m02example$BIC%in%BIC02)
  if(length(id)>3){
    lambda<-m02example$lambda[2,id]
    lambda02[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda02[1:3]<-m02example$lambda[2,id]
      lambda02<-na.omit(lambda02)
  }
  
############################## 12 ##############################################
BIC12<-sort(m12example$BIC[m12example$converged==1])[1:3]
BIC12<-na.omit(unique(BIC12))
  
  id<-which(m12example$BIC%in%BIC12)
  if(length(id)>3){
    lambda<-m12example$lambda[3,id]
    lambda12[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda12[1:3]<-m12example$lambda[3,id]
      lambda12<-na.omit(lambda12)
  }
  
lambda01
lambda02
lambda12
```
Note that for each transition, we reached the minimum as we have this U-shape of BIC values along $\lambda$. Once we have determined each value $\lambda$, we have 27 combinations of $\lambda_{01}$, $\lambda_{02}$ and $\lambda_{12}$ for $a=1$. Now, we can estimate the full model and ultimately select the combination $(\lambda_{01},\lambda_{02},\lambda_{12})$ that minimizes the BIC for lasso penalty ($a=1$). 

```{r,eval=F}
   f02<-as.formula(paste0("Hist(time = observed.lifetime, event = seen.exit) ~",paste0(paste0("X",seq(1:50)),collapse="+")))
  f01<-as.formula(paste0("Hist(time = list(L,R), event = seen.ill) ~",paste0(paste0("X",seq(1:50)),collapse="+")))
  f12<-as.formula(paste0("~",paste0(paste0("X",seq(1:50)),collapse="+")))

  modelexample <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=simu$data,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                lambda01 = lambda01,
                                lambda12= lambda12,
                                lambda02=lambda02,B=c(start,rep(0,n_var*2)),
                                nproc=2,clustertype = "PSOCK",
                                alpha=alpha_all,maxiter=100,maxiter.pena = 2)
  
  
```

```{r}
modelexample<-HIDeM::modelexample
summary(modelexample)
min(modelexample$BIC)
modelexample$lambda[,which.min(modelexample$BIC)]


coef01<-modelexample$coef[1:50,which.min(modelexample$BIC)]
coef01<-names(coef01[coef01!=0])

coef02<-modelexample$coef[51:100,which.min(modelexample$BIC)]
coef02<-names(coef02[coef02!=0])

coef12<-modelexample$coef[101:150,which.min(modelexample$BIC)]
coef12<-names(coef12[coef12!=0])
```


Based on the variable selection made in Reg IDM-ICT, we can re-estimate the model : 

```{r,eval=F}

# formula on each transition
  f02<-as.formula(paste0("Hist(time = observed.lifetime, event = seen.exit) ~",paste0(coef02,collapse="+")))
  f01<-as.formula(paste0("Hist(time = list(L,R), event = seen.ill) ~",paste0(coef01,collapse="+")))
  f12<-as.formula(paste0("~",paste0(coef12,collapse="+")))

  #starting point
  start<-modelexample$coef[,which.min(modelexample$BIC)]
  start<-start[start!=0]
  start<-c(modelexample$theta01[,which.min(modelexample$BIC)],
                                                      modelexample$theta02[,which.min(modelexample$BIC)],
                                                      modelexample$theta12[,which.min(modelexample$BIC)],start)
  
  #re-estimation
  remodelexample <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=simu$data,
                                eps=c(7,4,2),
                                method="splines",B=start,
                                maxiter=100)
  

  
  
```

```{r}
remodelexample<-HIDeM::remodelexample
summary(remodelexample)
print(remodelexample)

```

As we are in simulation setting, we can look at the Mean Square Error on the probability for a healthy individual of becoming diseased at a time $u$ between 0 and t, 
$$\displaystyle{\widehat{MSEP}=\frac{1}{N}\sum_{i=1}^{N}(\widehat F_{01i}(t_i) -  F_{01i}(t_i))^2}$$
where $N$ is the number of individuals, $t$ the time of first event between the illness, the death illness-free and the administrative censoring ($t$=min\{$T^{01},T^{02},18$\}), $\widehat F_{01i}(t_i)$ the estimated probability for individual $i$ of having the diseased until time $t_i$ and $ F_{01i}(t_i)$ the respective true probability modeled in the simulation. Note: $\widehat F_{01i}(t_i)=\int_0^{t_i}e^{-\widehat A_{01i}(u)-\widehat A_{02i}(u)}\widehat \alpha_{01i}(u)du$

To avoid overoptimism in predictive abilities, we need to use a test replicate and calculate the corresponding $\widehat{MSEP}$ on it. Firstly we simulate the test replicate using HIDeM::simulateIDM with a different seed.
```{r}
rep<-3
datatest<-HIDeM::simulateIDM(n=2000,seed=rep,
                  scale.waittime=0.07,shape.waittime=3.4,
                  scale.lifetime=0.085,shape.lifetime=3.4,
                  scale.illtime=0.075,shape.illtime=3.4,
                  prob.censoring=0.05,
                  n.inspections=8,
                  administrative.censoring = 18,
                  schedule=2.5,punctuality=0.5,nvar=n_var,mean=rep(0,n_var),cov=cov,
                  x01=id01,x02=id02,x12=id12,
                  beta01=BETA01[BETA01!=0],beta02=BETA02[BETA02!=0],
                  beta12=BETA12[BETA12!=0])
```

Following using HIDeM::intensity and pracma::gauss_kronrod we can calculate $\widehat F_{01}(t)$ for all individuals : 
```{r}
datatest<-datatest$data
F01<-trueF01<-rep(NA,2000)
time<-sapply(1:dim(datatest)[1],FUN=function(x){
     min(datatest$T01[x],datatest$T02[x],datatest$administrative.censoring[x])
   })


modelPar<-c(3.4,0.075,3.4,0.085,3.4,0.07)

library(pracma)

 for(i in 1:2000){
   
   # as time = 0 we have denum = 1 but in  other cases you can calculate
   # the left truncation using the following code of denum 
   
  beta01<-remodelexample$coef[1:remodelexample$NC[1]]
  b01<-sum(datatest[i,colnames(datatest)%in%remodelexample$Xnames01]*beta01)
  b01true<-sum(datatest[i,colnames(datatest)%in%paste0("X",c(1:50))]*BETA01)
  
      denum<-HIDeM::intensity(times=0,
                       knots=remodelexample$knots01,
                       theta=remodelexample$theta01,
                       linear.predictor = b01,
                       number.knots = remodelexample$nknots01,
                       method="splines")$survival
      
  beta02<-remodelexample$coef[(remodelexample$NC[1]+1):(remodelexample$NC[2]+remodelexample$NC[1])]
  b02<-sum(datatest[i,colnames(datatest)%in%remodelexample$Xnames02]*beta02)
  b02true<-sum(datatest[i,colnames(datatest)%in%paste0("X",c(1:50))]*BETA02)
  
      denum<-denum*intensity(times=0,
                             knots=remodelexample$knots02,
                             theta=remodelexample$theta02,
                             number.knots = remodelexample$nknots02,
                             linear.predictor = b02,
                             method="splines")$survival

    
      if(time[i]>0){
      num<- gauss_kronrod(f=function(x){

        res<-intensity(times=x,
                       knots=remodelexample$knots01,
                       theta=remodelexample$theta01,
                       linear.predictor = b01,
                       number.knots = remodelexample$nknots01,
                       method="splines")$intensity
        
        res<-res*intensity(times=x,
                           knots=remodelexample$knots01,
                           theta=remodelexample$theta01,
                           linear.predictor = b01,
                           number.knots = remodelexample$nknots01,
                           method="splines")$survival
        res<-res*intensity(times=x,
                           knots=remodelexample$knots02,
                           theta=remodelexample$theta02,
                           number.knots = remodelexample$nknots02,
                           linear.predictor = b02,
                           method="splines")$survival
        
        return(res)
      },a=0,b=time[i])$value
      
      truenum<- gauss_kronrod(f=function(x){

        res<-intensity(times=x,
                       theta=modelPar[1:2],
                       linear.predictor = b01true,
                       method="weib")$intensity
        
        res<-res*intensity(times=x,
                           theta=modelPar[1:2],
                           linear.predictor = b01true,
                           method="weib")$survival
        res<-res*intensity(times=x,
                           theta=modelPar[3:4],
                           linear.predictor = b02true,
                           method="weib")$survival
        
        return(res)
      },a=0,b=time[i])$value
      }else{num<-0}
      
      F01[i]<-(num/denum)
      trueF01[i]<-truenum
      
 }

sum(abs(F01-trueF01)^2)/2000
```
