---
title: "Example of regularized illness-death model on Paquid data set"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reg-IDM-ICT-Paq1000}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load HIDeM and Paq1000 data set

The Paquid data set composed of 1000 subjects selected randomly from the Paquid data set of 3675 subjects. We have one row per individual observation and the following 8 columns : 

- dementia for dementia status, 0=non-demented, 1=demented
- death for death status, 0=alive, 1=dead
- e, the age at entry in the study
- l : age at the last visit before the diagnostic of dementia or age at last visit for non-demented subjects
- r : age at the diagnostic visit for demented subject or age at the last visit for non-demented subjects
- t : age at death or age at the latest news for alive subject
- certif : primary school certificate, 0=without certificate, 1=with certificate
- gender: 0=female, 1=male

In addition, we had fifty noise variable noted Z, following an independent Gaussian distribution (centered and reduced). 

```{r setup}
library(HIDeM)
library(MASS)
library(gtsummary)
library(gt)
library(dplyr)

# Load the data (assuming it's a space-separated or tab-delimited file)
Paq1000 <- HIDeM::Paq1000

summaries<-Paq1000 %>%
   mutate(dementia = ifelse(dementia==1,"Demented","Healthy"),
          death=ifelse(death==1,"Death","Alive"),
          certif=ifelse(certif==1,"with certificate","without certificate"),
          gender=ifelse(gender==0,"female","male"))%>%
   tbl_strata(
     strata = dementia,
     .tbl_fun =
       ~ .x %>%
       tbl_summary(by = death,
                   type = list(where(is.numeric) ~ "continuous2"),
                   statistic = list(
                     all_categorical() ~ "{n} ({p}%)"
                   ),
                   digits = all_continuous() ~ 2),
     .header = "**{strata}**, N = {n}"
   ) %>%
    modify_caption("Characteristics of individuals in Paq1000 dataset")

summaries
Z<-MASS::mvrnorm(n = 1000, mu = rep(0,50), Sigma = diag(50))
Z<-as.data.frame(Z)
colnames(Z)<-paste0("Z",c(1:50))

Paq1000<-cbind(Paq1000,Z)
```


## Run IDM-ICT 

In this section, we will explicit the profile likelihood, with:

- an outer loop on penalty parameters noted $(a,\lambda_{01},\lambda_{02},\lambda_{12})$, and 
- an inner loop on regression parameters $(\beta_{01},\beta_{02},\beta_{12})$ and baseline intensity parameters $(\theta_{01},\theta_{02},\theta_{12})$

Firstly, we need to perform a pre-selection of penalty parameters for each transition separately. For each transition, we first fit multi-state models including covariates only in the transition from state $h$ to $l$, and considering a grid of $\lambda_{hl}$ with equidistant values from  0.0001 and 100 while keeping $a$ fixed at 1. It is recommended to try multiple values of $a$ in $]0,1]$, but for this example we will limit to lasso penalty (a=1). 

We choose to estimate the baseline intensity transition with M-spline basis with nodes at 65, 84 and 103 years old. To initiative, baseline intensities parameters of M-splines, we run a model without covariates. 

1. Choose baseline intensity parametrization based on void model
```{r,eval=F}


mvoidPaq1000 <-  HIDeM::idm(formula02=Hist(time=t,event=death,entry=e)~certif+gender,
                        formula01=Hist(time=list(l,r),event=dementia)~certif+gender,
                        formula12=~certif+gender,
                        method="splines",
                        data=Paq1000,maxiter=100)

mvoidquant <-  HIDeM::idm(formula02=Hist(time=t,event=death,entry=e)~1,
                        formula01=Hist(time=list(l,r),event=dementia)~1,
                        formula12=~1,
                        method="splines",n.knots = c(3,3,3),knots="quantile",
                     type.quantile=1,
                        data=Paq1000,maxiter=100)

-2*mvoid$loglik 
-2*mvoidquant$loglik 

mvoidn4 <-  HIDeM::idm(formula02=Hist(time=t,event=death,entry=e)~1,
                        formula01=Hist(time=list(l,r),event=dementia)~1,
                        formula12=~1,
                        method="splines",n.knots = c(4,4,4),
                        data=Paq1000,maxiter=100)

mvoidquantn4 <-  HIDeM::idm(formula02=Hist(time=t,event=death,entry=e)~1,
                        formula01=Hist(time=list(l,r),event=dementia)~1,
                        formula12=~1,
                        method="splines",n.knots = c(4,4,4),knots="quantile",
                     type.quantile=1,
                        data=Paq1000,maxiter=100)

-2*mvoid$loglik +2*(3*5)
-2*mvoidn4$loglik +2*(3*6)

-2*mvoidquant$loglik +2*3*5
-2*mvoidquantn4$loglik +2*3*6

# best to keep 5 parameters per transition using equidistant points

```

2. Estimation of Reg IDM-ICT transition specific model 
```{r,eval=F}
a<-1

start<-c(mvoidPaq1000$theta01,mvoidPaq1000$theta02,mvoidPaq1000$theta12,rep(0,52))
  
  nlambda<-20
  lambdatest<-seq(0.01,100,length.out=nlambda)
  penalty<-ifelse(a==1,"lasso","elasticnet")

  
############################ 01 ################################################
    f02<-as.formula("Hist(time = t, event =death,entry=e) ~1")
  f01<-as.formula(paste0("Hist(time = list(l,r), event = dementia) ~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f12<-as.formula("~1")
  
  m01Paq1000 <-HIDeM::  idm(formula02 = f02,
                                    formula01 = f01,
                                    formula12 = f12,data=Paq1000,
                                    penalty=penalty,eps=c(7,4,1),
                                    lambda01 = lambdatest,
                                    lambda02=0.0001,
                                    lambda12=0.0001,B=start,
                                method="splines",
                                alpha=k,maxiter=100,maxiter.pena = 2)
  

################################ 02 ############################################

  f02<-as.formula(paste0("Hist(time = t, event = death,entry=e) ~ certif + gender + ",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f01<-as.formula("Hist(time = list(l,r), event = dementia) ~ 1")
  f12<-as.formula("~1")
#setwd("C:/Users/ab17/Desktop/CURTA/SMOOTH_HAZARD/OPTIM_B_DIFFLAMBDA_derivaana_all/Weibull_simu/Scenario1")

  m02Paq1000 <-HIDeM::  idm(formula02 = f02,
                                    formula01 = f01,
                                    formula12 = f12,data=Paq1000,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                    lambda02 = lambdatest,
                                    lambda01=0.0001,
                                    lambda12=0.0001,B=start,
                                alpha=k,maxiter=100,maxiter.pena = 2)
  


######################################## 12 ###################################

  f02<-as.formula("Hist(time = t, event = death,entry=e) ~1")
  f01<-as.formula("Hist(time = list(l,r), event =dementia) ~ 1")
  f12<-as.formula(paste0("~ certif + gender + ",paste0(paste0("Z",seq(1:50)),collapse="+")))

  m12Paq1000 <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=Paq1000,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                lambda01 = 0.0001,
                                lambda12= lambdatest,
                                lambda02=0.0001,B=start,
                                alpha=k,maxiter=100,maxiter.pena = 2)
  
  
```

The ouput of each models can be displayed using standard function such as print and summary : 
```{r,fig.width=6}

m01Paq1000<-HIDeM::m01Paq1000
m02Paq1000<-HIDeM::m02Paq1000
m12Paq1000<-HIDeM::m12Paq1000

#print(m01Paq1000)
#summary(m01Paq1000)

#print(m02Paq1000)
#summary(m02Paq1000)

#print(m12Paq1000)
#summary(m12Paq1000)
```
The following step is to visualize the Bayesian Indicator Criteria (BIC) and determine the 3 values of $\lambda$ per transition minimizing it : 

```{r,fig.width=6,fig.height=6,fig.alt="BIC display"}

plot(m01Paq1000$lambda[1,],m01Paq1000$BIC,xlab="Lambda values for 0 -> 1",ylab="BIC")
plot(m02Paq1000$lambda[2,],m02Paq1000$BIC,xlab="Lambda values for 0 -> 2",ylab="BIC")
plot(m12Paq1000$lambda[3,],m12Paq1000$BIC,xlab="Lambda values for 1 -> 2",ylab="BIC")

lambda01<-lambda02<-lambda12<-rep(NA,3)

############################## 01 ##############################################
BIC01<-sort(m01Paq1000$BIC[m01Paq1000$converged==1])[1:3]
BIC01<-na.omit(unique(BIC01))
  
  id<-which(m01Paq1000$BIC%in%BIC01)
  if(length(id)>3){
    lambda<-m01Paq1000$lambda[1,id]
    lambda01[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda01[1:3]<-m01Paq1000$lambda[1,id]
      lambda01<-na.omit(lambda01)
  }
  
############################## 02 ##############################################
BIC02<-sort(m02Paq1000$BIC[m02Paq1000$converged==1])[1:3]
BIC02<-na.omit(unique(BIC02))
  
  id<-which(m02Paq1000$BIC%in%BIC02)
  if(length(id)>3){
    lambda<-m02Paq1000$lambda[2,id]
    lambda02[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda02[1:3]<-m02Paq1000$lambda[2,id]
      lambda02<-na.omit(lambda02)
  }
  
############################## 12 ##############################################
BIC12<-sort(m12Paq1000$BIC[m12Paq1000$converged==1])[1:3]
BIC12<-na.omit(unique(BIC12))
  
  id<-which(m12Paq1000$BIC%in%BIC12)
  if(length(id)>3){
    lambda<-m12Paq1000$lambda[3,id]
    lambda12[1:3]<-sort(lambda)[1:3]
  }else{
    
      lambda12[1:3]<-m12Paq1000$lambda[3,id]
      lambda12<-na.omit(lambda12)
  }
  
lambda01
lambda02
lambda12
```
Note that for each transition, we reached the minimum as we have this U-shape of BIC values along $\lambda$. Once we have determined each value $\lambda$, we have 27 combinations of $\lambda_{01}$, $\lambda_{02}$ and $\lambda_{12}$ for $a=1$, leading to $108$ combinations in total. Now, we can estimate the full model and ultimately select the combination $(a,\lambda_{01},\lambda_{02},\lambda_{12})$ that minimizes the BIC. 

3. Estimate Reg IDM-ICT with variable selection on all transitions
```{r,eval=F}
   f02<-as.formula(paste0("Hist(time = t, event = death,entry=e) ~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f01<-as.formula(paste0("Hist(time = list(l,r), event = dementia) ~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f12<-as.formula(paste0("~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))

  modelPaq1000 <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=Paq1000,
                                penalty=penalty,eps=c(7,4,1),
                                method="splines",
                                lambda01 = lambda01,
                                lambda12= lambda12,
                                lambda02=lambda02,B=c(start,rep(0,52*2)),
                                alpha=k,maxiter=100,maxiter.pena = 2)
  
  
  
  
```
```{r}

modelPaq1000<-HIDeM::modelPaq1000

summary(modelPaq1000)

min(modelPaq1000$BIC)
modelPaq1000$lambda[,which.min(modelPaq1000$BIC)]

# no variable on 0 --> 1
coef01<-modelPaq1000$coef[1:52,which.min(modelPaq1000$BIC)]
coef01<-names(coef01[coef01!=0])
# gender on 0 --> 2 
coef02<-modelPaq1000$coef[53:104,which.min(modelPaq1000$BIC)]
coef02<-names(coef02[coef02!=0])

# no variable on 1 -->2
coef12<-modelPaq1000$coef[105:156,which.min(modelPaq1000$BIC)]
coef12<-names(coef12[coef12!=0])
```

4. Estimate covariate effects 

Based on the variable selection made in Reg IDM-ICT, we can re-estimate the model : 

```{r,eval=F}
   f02<-as.formula(paste0("Hist(time = t, event = death,entry=e) ~ gender"))
  f01<-as.formula(paste0("Hist(time = list(l,r), event = dementia) ~ 1"))
  f12<-as.formula(paste0("~ 1"))

  remodelPaq1000 <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=Paq1000,
                                eps=c(7,4,2),
                                method="splines",
                                lambda02=lambda02,B=c(mvoidPaq1000$theta01,
                                                      mvoidPaq1000$theta02,
                                                      mvoidPaq1000$theta12,0),
                                maxiter=100,maxiter.pena = 2)
  
  
  
```

```{r,fig.width=6}
remodelPaq1000<-HIDeM::remodelPaq1000
summary(remodelPaq1000)
print(remodelPaq1000)
```

To evaluate the stability of the variable selection for given penalty parameters, we can perform boostrap on individuals. As an illustration we will perform it on 50 samples, 

```{r,eval=F}
mvoidPaq1000<-HIDeM::mvoidPaq1000
start<-c(mvoidPaq1000$theta01,mvoidPaq1000$theta02,mvoidPaq1000$theta12,rep(0,52*3))
lambda01<-modelPaq1000$lambda[1,which.min(modelPaq1000$BIC)]
lambda02<-modelPaq1000$lambda[2,which.min(modelPaq1000$BIC)]
lambda12<-modelPaq1000$lambda[3,which.min(modelPaq1000$BIC)]

bootmodel<-list()
length(bootmodel)<-50
for (k in 1:50){
  
  set.seed(k)
  print(k)
  id<-sample(c(1:dim(Paq1000)[1]),size=dim(Paq1000)[1],replace=T)
  boot<-Paq1000[id,]
  
  
     f02<-as.formula(paste0("Hist(time = t, event = death,entry=e) ~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f01<-as.formula(paste0("Hist(time = list(l,r), event = dementia) ~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))
  f12<-as.formula(paste0("~ certif + gender +",paste0(paste0("Z",seq(1:50)),collapse="+")))

  modelPaq1000 <-HIDeM::  idm(formula02 = f02,
                                formula01 = f01,
                                formula12 = f12,data=boot,
                                penalty="lasso",eps=c(7,4,1),
                                method="splines",
                                lambda01 = lambda01,
                                lambda12= lambda12,
                                lambda02=lambda02,B=start,
                                alpha=1,maxiter=100,maxiter.pena = 2)
  bootmodel[[k]]<-modelPaq1000
  

}
```
```{r,fig.width=6,fig.height=6, fig.alt="Bootstrap variable selection"}
allboot<-NULL
library(ggplot2)

for(k in 1:50){
  
  ########################### all ######################################
  modelPaq1000<-HIDeM::bootPaq1000[[k]]
  set<-k

  bootk<-data.frame(coef=as.vector(modelPaq1000$coef),
                  names=rownames(modelPaq1000$coef),
                  transition=c(rep("01",length(unique(rownames(modelPaq1000$coef)))),rep("02",length(unique(rownames(modelPaq1000$coef)))),
                               rep("12",length(unique(rownames(modelPaq1000$coef))))),
                               
                  id=rep(k,dim(modelPaq1000$coef)[1]))
  
  ##################### combine ############################
  allboot<-rbind(bootk,allboot)
  
  
}
 
  test<-aggregate(data=allboot,coef~transition+names,FUN=function(x){sum(x!=0)})
  test$coef<-test$coef/50
  
  plot<-test[test$transition=="01",]
  plot<-plot[order(plot$coef),]
  plot$order<-c(1:dim(plot)[1])
  labs<-plot$names
    
  p01<-ggplot(plot,aes(x=coef,y=as.factor(order)))+geom_bar(position = position_dodge(),
                    stat="identity",
                   color = "black",alpha=0.5)+theme_classic()+
    scale_y_discrete(name="Variable",breaks=c(1:dim(plot)[1]),
                     labels=labs)+facet_grid(~transition,labeller = as_labeller(c(`01`="Healthy to dementia",`02`="Healthy to death",`12`="Dementia to death")),scales="free_x")+theme_classic()+
    geom_vline(xintercept = 1,color="red")+xlab(" %selected (50 replicates)")
    
    
  plot<-test[test$transition=="02",]
  plot<-plot[order(plot$coef),]
  plot$order<-c(1:dim(plot)[1])
  labs<-plot$names
 
  p02<-ggplot(plot,aes(x=coef,y=as.factor(order)))+geom_bar(position = position_dodge(),
                    stat="identity",
                   color = "black",alpha=0.5)+theme_classic()+
    scale_y_discrete(name=" ",breaks=c(1:dim(plot)[1]),
                     labels=labs)+ facet_grid(~transition,labeller = as_labeller(c(`01`="Healthy to dementia",`02`="Healthy to death",`12`="Dementia to death")),scales="free_x")+
  geom_vline(xintercept = 1,color="red")+xlab("%selected (500 replicates)")

  plot<-test[test$transition=="12",]
  plot<-plot[order(plot$coef),]
  plot$order<-c(1:dim(plot)[1])
  labs<-plot$names

 
  p12<-ggplot(plot,aes(x=coef,y=as.factor(order)))+geom_bar(position = position_dodge(),
                    stat="identity",
                   color = "black",alpha=0.5)+theme_classic()+
    scale_y_discrete(name=" ",breaks=c(1:dim(plot)[1]),
                     labels=labs)+ facet_grid(~transition,labeller = as_labeller(c(`01`="Healthy to dementia",`02`="Healthy to death",`12`="Dementia to death")),scales="free_x")+
  geom_vline(xintercept = 1,color="red")+xlab("%selected (500 replicates)")
p01
p02
p12

```


